\maketitle
\makedeclaration

\begin{abstract} % 300 word limit

Two searches for Beyond Standard Model resonances are performed                                                                                 %% 9
%decaying to a pair of $b$-quarks or a $b$-quark and a gluon are performed.                                                                     %%%%%
using 13~TeV \mbox{proton--proton} collision data collected by the ATLAS detector in 2015 and 2016                                              %% 16
using the invariant mass distribution of pairs of jets,                                                                                         %% 9
where at least one or both jets are identified as containing a \mbox{$b$-quark}.                                                                %% 13
The searches are sensitive to resonances decaying to a pair of \mbox{$b$-quarks} or a \mbox{$b$-quark} and a gluon.                             %% 18
A high-mass search probes the mass region 1.4~--~6~TeV using a data-set corresponding to an integrated luminosity of 13.3~\ifb{}.               %% 22
A low-mass search utilises real-time $b$-jet identification to                                                                                  %% 10
probe the mass region 0.6~--~1.5~TeV using a data-set corresponding to an integrated luminosity of 24.3~\ifb{}.                                 %% 18
No evidence of a resonance is found.                                                                                                            %% 7
Excited $b^*$ quarks with masses from 1.4 to 2.3~TeV and                                                                                        %% 11                        
a set of $Z'$ boson models with masses from 0.6 to 1.25~TeV or at 1.5~TeV are excluded at the 95\% credibility-level.                           %% 24
In addition, 95\% credibility-level upper limits are set on generic signals with a Gaussian distribution in the mass range 0.65~--~6~TeV.               %% 20

\end{abstract}                                                                                                                                  %% == 177

\begin{acknowledgements}

%% Andreas
I would like to thank Andreas for always being eager to provide advice, support and macchiatos.
Your supervision has made this thesis possible and is greatly appreciated.

%% Di-b-jet
Thanks to Rui, Andrea, Bing, Nishu, Sergei, Jeff, Jimmy and all those I worked with in the di-$b$-jet analysis team;
I hope that your hard work is given justice in this thesis.

%% ATLAS postdocs
I would also like to thank all the students, fellows and post-docs at ATLAS and UCL who provided help throughout my PhD;
the way that so many are always willing to drop what they are doing to aid another is something that makes ATLAS a great collaboration to be a part of.
Particular thanks go to Kate, John and Gabriel for always providing help and guidance when I needed it.
Also thanks to Andy and Jiggins for putting up with me in the office for so long and answering every one of my inane questions.

%% Family
Thanks to my family and friends in Manchester, Glasgow, London and Geneva who have made the last three and a bit years an enjoyable experience.

%% Parents
Finally, a huge thanks to my parents who always supported and encouraged me;
without you this wouldn't have been possible. 

\end{acknowledgements}

\setcounter{tocdepth}{2} 
% Setting this higher means you get contents entries for
%  more minor section headers.

\tableofcontents
\listoffigures
\listoftables

