\chapter{Conclusions}
\label{sec:conc}

Two searches for Beyond Standard Model (BSM) resonances in the invariant mass of pairs of jets,
where at least one or both jets contain a $b$-quark,
have been performed using 13~TeV $pp$ collision data collected by the ATLAS detector.
Such searches are sensitive to BSM resonances that preferentially decay to one or two $b$-quarks, such as the excited $b^*$ quark and the $Z'$ boson.

%The first di-$b$-jet search probes the mass region 1.4-6~TeV
%13~TeV $pp$ collisions collected in 2015 and 2016 by the ATLAS detector with an integrated luminosity of 13.3~\ifb{}.
%Dijet events where one or both jets has been identified as a $b$-jet have been considered.

A high-mass di-$b$-jet search probes the mass region 1.4~--~6~TeV
%in the $\geq1$ and 2 $b$-tag categories
using data collected in 2015-16 with an integrated luminosity of 13.3~\ifb{}.
No evidence of a BSM resonance is found.
The excited $b^*$ quark with a mass in the interval 1.4~--~2.3~TeV
and the leptophobic $Z'$ boson with a mass of 1.5~TeV are excluded at the 95\% credibility level.
95\% credibility level upper limits on $\sigma\,\text{x}\,\mathit{A}\,\text{x}\,\epsilon\,\text{x}\,\mathit{BR}$
are set in the range 0.2 to 0.001 pb for generic Gaussian signals with widths from 15\% to 3\% and masses in the interval 1.4~--~6~TeV.
This di-$b$-jet search has been published as a conference note~\cite{dibjet-ichep_conf}.

A low-mass di-$b$-jet search probes the mass region 0.6~--~1.5~TeV
%in the 2 $b$-tag category
using data collected using the ATLAS $b$-jet trigger in 2016 with an integrated luminosity of 24.3~\ifb{}.
No evidence of a BSM resonance is found.
The sequential standard model and leptophobic $Z'$  boson models with a mass in the interval 0.6~--~1.25~TeV
and a Dark Matter inspired $Z'$ boson model with a mass in the interval 0.6~--~1.0~TeV are excluded at the 95\% credibility level.
95\% credibility level upper limits on $\sigma\,\text{x}\,\mathit{A}\,\text{x}\,\epsilon\,\text{x}\,\mathit{BR}$ in the range 0.05 to 0.003 pb
are set for generic Gaussian signals with widths from 15\% to 0\% and masses in the interval 0.65~--~1.4~TeV.
This di-$b$-jet search is soon to be published.

The low-mass di-$b$-jet search uses the ATLAS $b$-jet trigger; therefore a detailed understanding of the $b$-jet trigger performance is required.
It was identified that some regions of data collected by the ATLAS $b$-jet trigger in 2016 were defective
and a strategy was developed to mitigate the observed issues.
Then, a measurement of the $b$-jet trigger efficiency in 2016 data was performed.
The $b$-jet trigger studies and efficiency measurement presented in this thesis will be used by a number of other ATLAS analyses,
such as a proposed update to a search for resonances decaying to 4 $b$-quarks via a pair of Higgs bosons~\cite{trig-H4b} using 2016 data.

The outlook for future di-$b$-jet searches at the ATLAS detector has been considered,
including a summary of the prospects for di-$b$-jet searches at high luminosities
and a discussion of possible future developments to further develop the analyses presented in this thesis.


